Methods for Large Scale Learning to Rank

### 2014-04-09 report/Chapters/CrossBenchmarkComparison.tex
verhaal MAP-results

%TODO: Wat valt er te zeggen over de NDCG@10 resultaten? %

@@

%TODO: Wat valt er te zeggen over de MAP resultaten? %

>>>>

@@

Where comparisons on the \ac{nDCG}-metric at different cut-off points where highly in agreement in terms of the best performing algorithms, the comparison in terms of \ac{MAP} shows different results. RankDE scores a Normalised Winning Number of 1.0 on one dataset, like LambdaNeuralRank did on for all \ac{nDCG}-comparisons. In contrast to LambdaNeuralRank, RankDE achieved this highest score on the LETOR 2.0 TD2003, a dataset on which many methods are evaluated.\\

LARF and LRUF score very high Normalised Winning Number scores, but based on only relatively few datasets, just as in the \ac{nDCG}-comparisons. Notable is that SmoothRank and ListNet, which showed both high accuracy and high certainty on all \ac{nDCG}-comparisons, are not within the best performing methods in the \ac{MAP}-comparison. A deeper look in the raw data Tables \ref{tab:raw_data_norm_winnum_ndcg3} to \ref{tab:raw_data_norm_winnum_map} in Appendices \ref{app:norm_winnum_ndcg3} to \ref{app:norm_winnum_map} shows that LAC-MR-OR is evaluated on many more datasets for \ac{MAP} compared to \ac{nDCG}, which resulted in LAC-MR-OR obtaining equal certainty to ListNet with a higher Normalised Winning Number. SmoothRank performed a Normalised Winning Number of around 0.53 over 7 datasets, which is still good in both certainty and accuracy, but not among the top methods. RE-QR is one of the best performers in the \ac{MAP}-comparison with a reasonable amount of benchmark evaluations. No reported \ac{nDCG} performance was found in the literature study for RE-QR. There is a lot of certainty on the accuracy of RankBoost and Rank\ac{SVM} as both models are evaluated on the majority of datasets included in the comparison for the \ac{MAP}-metric, but given their Normalised Winning Number it can said that both methods are not within the top performing Learning-to-Rank methods.
